---
title: "Genuary Day 1"
output:
  html_document:
    css: style_7.css
    df_print: paged
    theme: flatly
    highlight: breezedark
    toc_float: yes
    code_download: yes
    word_document: null
    toc: yes
---

Genuary Day 1:

Tried to modify [Georgios Karamanis code](https://github.com/gkaramanis/aRtist/blob/main/genuary/2022/2022-01/2022-01.R), see what comes of it and learn in the process. Thank you Georgios 🙇.

```{r}
suppressWarnings(if (!require(pacman)) install.packages("pacman"))

pacman::p_load('tidyverse', 'ggforce', 'ambient', 'here', 'paletteer')

# Not on cran
library(MetBrewer)

```

-   `ggforce` aims to be a collection of mainly new stats and geoms for composing specialised ggplot plots.

-   `ambient` is a an R package that provides access to the [FastNoise](https://github.com/Auburns/FastNoise) C++ library for generating noise.

-   `MetBrewer` is a collection of Palettes inspired by works at the Metropolitan Museum of Art in New York.

```{r}
set.seed(2056)

# Create a long format grid
grid <- long_grid(seq(1, 10, length.out = 100), seq(1, 10, length.out = 100))
# Generate perlin noise
grid$noise <- gen_perlin(grid$x, grid$y, frequency = 0.5)

grid %>% 
  slice_at()
```

Just a data frame with x, y and some noise. Good to know.

`ambient::long_grid()` : Create a long format grid. Somewhat similar to `tidyr::crossing`?

Time to plot it.

[`ggforce::geom_regon`](https://ggforce.data-imaginist.com/reference/geom_regon.html) : makes it easy to construct regular polygons (polygons where all sides and angles are equal) by specifying the number of sides, position, and size.

```{r}
grid <- long_grid(seq(1, 12, length.out = 100), seq(1, 10, length.out = 100))
# Generate perlin noise
grid$noise <- gen_perlin(grid$x, grid$y, frequency = 2)

grid %>% 
  ggplot() +
  geom_regon(aes(x0 = x, y0 = y, sides = 8, angle = noise * pi, r = 2.5, fill = noise), size = 0.1, color = NA, alpha = 0.1) +
  # Use your own colour scale with gradientn
  scale_fill_gradientn(colors = rev(met.brewer("Hiroshige"))) +
  coord_cartesian(clip = "off") +
  theme_void() +
  theme(
    legend.position = "none",
    plot.background = element_rect(fill = "white", color = NA)
  )
```

```{r}
# ggsave("novus_1.png", device = "png", width = 12, height = 12, units = "in", dpi = 500)

ggsave("novus_3_1.png", device = "png",  width = 20, height = 11.25, dpi = 700)
```
